Field-informed Reinforcement Learning for Learnining Large Scale Collective Tasks

### 2023-05-03 paper.tex
feat: on GNN

\usepackage[T1]{fontenc}
\usepackage{xcolor}
\usepackage{cleveref}
\usepackage{acronym}
\def\doi#1{\href{https://doi.org/\detokenize{#1}}{\url{https://doi.org/\detokenize{#1}}}}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}
%
\usepackage{listings}
\lstset{language=Pascal}
\begin{document}
%
\title{Field-informed Reinforcement Learning for Learnining Large Scale Collective Tasks} %% Todo improve
% or: Field-Informed Reinforcement Learning: A Scalable and Effective Method for Collective Intelligence
% or: A Novel Approach to Reinforcement Learning for Adaptive Collective Systems
%

@@

%%% Comment command, to be removed before submission
\newcommand{\meta}[3]{\textcolor{#1}{\textbf{#2}: #3}}
\newcommand{\ga}[1]{\meta{red}{GA}{#1}}
\newcommand{\lukas}[1]{\meta{purple}{Lukas}{#1}}
\newcommand{\mv}[1]{\meta{green}{MV}{#1}}
\ga{Page limit: 10 pages (include refs)}

\acrodef{DecPOMDP}[DecPOMDP]{decentralized partially observable Markov decision processes}
\acrodef{RL}[RL]{reinforcement learning}
\acrodef{MARL}[MARL]{multi-agent reinforcement learning}
\begin{abstract}
Coordinatinating a group of intelligent agents in multi-agent systems 
 is a research problem that has been addressed for a long time, 
 due to the challenges posed by distribution and of the definition of distributed intelligence. 
%
The problem is even more evident in collective adaptive systems, 
 where the scale of the systems considered makes the definition of collective behaviors even more challenging.

@@

\begin{IEEEkeywords}
aggregate computing, Graph Neural Network, Cyber-Physical Swarms.
\end{IEEEkeywords}
%
\section{Introduction}
Various phenomena in the real world are not evenly distributed across the environment such as watershed, wild fires, traffic, human crowd movement, or wild life movement from insects, fish, birds, and mammals.
To acquire appropriate information about such phenomena, we also need to distribute the sensors accordingly to cover all aspects sufficiently. While manual deployment will mitigate the problem, not all phenomena are known exactly \emph{a priori} and would require maintenance and adjustment during runtime. Even worse, with phenomena able to change their location, size, and distribution---as it is the case with crowds, wild life, or wild fires---an adaptation of the collective sensors is required in order to keep the required information.

@@

\section{Background and Motivation}
\label{sec:background}
\ga{Page budget: 1/2 page \\}
\ga{Plan: discussion about the problem of coordination in multi-agent systems 
and the need for a scalable approach. In doing this, we will discuss some of the existing approaches (declarative, RL and )}
\subsection{Field Coordination Approaches}
\ga{discussion about field used as a coordination mechanism in multi-agent systems. Introduction to AC}
\subsection{Graph Neural Networks for Multi-Agent Systems}
\subsection{Many-Agent Reinforcement Learning}
\ga{plan: we could discuss briefly about standard appraoch (few agents), mean field approach (many agents). This will led to our approach, which is a combination of DQN (or any Deep RL approach) and GNN.}

>>>>

\usepackage[T1]{fontenc}
\usepackage{xcolor}
\usepackage{acronym}
\usepackage{amsmath}
\def\doi#1{\href{https://doi.org/\detokenize{#1}}{\url{https://doi.org/\detokenize{#1}}}}
%
\usepackage{graphicx}

% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}
%
\usepackage{listings}

\usepackage{cleveref}
\lstset{language=Pascal}
\begin{document}
%
\title{Field-informed Reinforcement Learning for Learnining Large Scale Collective Tasks} %% Todo improve
% or: Field-Informed Reinforcement Learning: A Scalable and Effective Method for Collective Intelligence
% or: A Novel Approach to Reinforcement Learning for Adaptive Collective Systems
%

@@

%%% Comment command, to be removed before submission
\newcommand{\meta}[3]{\textcolor{#1}{\textbf{#2}: #3}}
\newcommand{\ga}[1]{\meta{red}{GA}{#1}}
\newcommand{\lukas}[1]{\meta{purple}{Lukas}{#1}}
\newcommand{\mv}[1]{\meta{green}{MV}{#1}}
\ga{Page limit: 10 pages (include refs)}
\acrodef{DecPOMDP}[DecPOMDP]{decentralized partially observable Markov decision processes}
\acrodef{RL}[RL]{reinforcement learning}
\acrodef{MARL}[MARL]{multi-agent reinforcement learning}
\begin{abstract}
Coordinatinating a group of intelligent agents in multi-agent systems 
 is a research problem that has been addressed for a long time, 
 due to the challenges posed by distribution and of the definition of distributed intelligence. 
%
The problem is even more evident in collective adaptive systems, 
 where the scale of the systems considered makes the definition of collective behaviors even more challenging.

@@

\begin{IEEEkeywords}
aggregate computing, Graph Neural Network, Cyber-Physical Swarms.
\end{IEEEkeywords}
%
\ga{Paper levels:
\begin{itemize}
  \item Distributed collective intelligence
  \item GNN and field coordination
  \item Spatial tracking
\end{itemize}
}
\section{Introduction}
Various phenomena in the real world are not evenly distributed across the environment such as watershed, wild fires, traffic, human crowd movement, or wild life movement from insects, fish, birds, and mammals.
To acquire appropriate information about such phenomena, we also need to distribute the sensors accordingly to cover all aspects sufficiently. While manual deployment will mitigate the problem, not all phenomena are known exactly \emph{a priori} and would require maintenance and adjustment during runtime. Even worse, with phenomena able to change their location, size, and distribution---as it is the case with crowds, wild life, or wild fires---an adaptation of the collective sensors is required in order to keep the required information.

@@

\section{Background and Motivation}
\label{sec:background}
\ga{Page budget: 1/2 page \\}
\ga{Plan: discussion about the problem of coordination in multi-agent systems 
and the need for a scalable approach. In doing this, we will discuss some of the existing approaches (declarative, RL and )}
\subsection{Field Coordination Approaches}
\ga{discussion about field used as a coordination mechanism in multi-agent systems. Introduction to AC}
\subsection{Graph Neural Networks}
Over the years, several different neural networks have been proposed to solve specific tasks. 
%
Whereas Convolutional Neural Networks are designed to be used with image and spatial-like data (e.g., audio),
 Graph Neural Networks (GNNs) are a novel model used to process graph-structured data. 
%
Let $ G = (V, E) $ be a graph, where $ V $ is the set of nodes and $ E $ is the set of edges. 
%
Given $X_v$ a feature vector associated to each node $v \in V$, 
 the goal of a GNN is to learn the node embedding $X'_v$ for each node $v \in V$.
 In modern GNNs, the node embedding $X'_v$ is computed by aggregating information from the node's neighbors $N(v)$,
  and then combining it with the node's current embedding $X_v$.
% 
Formally, a GNN can be defined by two phases:
\begin{equation}
a_{v}^{(k)}=\operatorname{AGGREGATE}^{(k)}\left(\left\{h_{u}^{(k-1)}: u \in \mathcal{N}(v)\right\}\right)   
\end{equation}
\begin{equation}
h_{v}^{(k)}=\operatorname{COMBINE}^{(k)}\left(h_{v}^{(k-1)}, a_{v}^{(k)}\right)
\end{equation}
where $h_{v}^{k}$ is the embedding of node $v$ at the $k$-th layer, 
 $\mathcal{N}(v)$ is the set of neighbors of node $v$ computed from $E$.
%
The differential part come into play in the $\operatorname{COMBINE}$ function, 
 which is usually a differentiable function such as a neural network layer.
%
$\operatorname{AGGREGATE} $ instea is a function that aggregates the information from the neighbors of a node $v$
  and it could be a simple sum or a more complex function such as a neural network layer.
%
This formulation allows GNNs to effectively process and extract features from graph-structured data by iteratively aggregating and transforming information from the node's neighbors.

GNN are used in several fields such as social network analysis, chemistry, and physics.
In this paper, we use GNNs to learn a local behavior for each agent in a multi-agent system (more details in Section~\ref{sec:approach}).
\subsection{Many-Agent Reinforcement Learning}
\ga{plan: we could discuss briefly about standard appraoch (few agents), mean field approach (many agents). This will led to our approach, which is a combination of DQN (or any Deep RL approach) and GNN.}
